General purpose gene annotation using deep learning

### 2020-02-04 paper/main.tex
deleted old csv data, some paper

\begin{table}[!t]
\processtable{Data group statistics for all data\label{Tab:statistics_all}} {
\begin{tabular}{@{}lll@{}}
\toprule & EnsemblMetazoa & JGI Phytosome\\
\midrule
Fraction of classes  & 0.6, 0.02, 0.1, 0.2 & 0.6, 0.02, 0.1, 0.2 \\
(Intergenic, UTR, CDS, Intron) & & \\
Geenuff error rate & 0.1 (+- 0.02) & 0.3 (+- 0.02) \\
Average genome size in Gbp& 1.1 (+- 0.5) & 0.3 (+- 0.1) \\
Average gene length & 23000 (+- 5000) & 3370 (+- 50) \\
\botrule
\end{tabular}}{Values are averages across all genomes of a data group}
\end{table}

\begin{table}[!t]
\processtable{Data group statistics for our training data\label{Tab:statistics_training}} {
\begin{tabular}{@{}lll@{}}
\toprule & EnsemblMetazoa & JGI Phytosome\\
\midrule
Fraction of classes  & 0.6, 0.02, 0.1, 0.2 & 0.6, 0.02, 0.1, 0.2 \\
(Intergenic, UTR, CDS, Intron) & & \\
Geenuff error rate & 0.1 (+- 0.02) & 0.3 (+- 0.02) \\
Average genome size in Gbp& 1.1 (+- 0.5) & 0.3 (+- 0.1) \\
Average gene length & 23000 (+- 5000) & 3370 (+- 50) \\
\botrule
\end{tabular}}{Values are averages across all genomes of a data group}
\end{table}

@@

\begin{table}[!t]
\processtable{Experimental Results and Comparison\label{Tab:03}} {
\begin{tabular}{@{}lll@{}}
\toprule & EnsemblMetazoa & JGI Phytosome\\
\midrule
Augustus & 0.62 (+-0.02) & 0.83 (+- 0.03)\\
Best Helixer model & 0.62 (+-0.02) & 0.72 (+-0.02) \\
Best model + varied input length & 0.62 (+-0.02) & 0.72 (+-0.02) \\
Best model + varied input length + overlapping & 0.62 (+-0.02) & 0.72 (+-0.02) \\
Varied input length + overlapping + ensembling & 0.62 (+-0.02) & 0.72 (+-0.02) \\
\botrule
\end{tabular}}{Values are averages in CDS F1 (?) across all validation and test genomes of the \\ respective group.}
\end{table}

@@

>>>>

\begin{table}[!t]
\processtable{Data group statistics for all data\label{Tab:statistics_all}} {
\begin{tabular}{@{}lll@{}}
\toprule & EnsemblMetazoa & JGI Phytosome\\
\midrule
Fraction of classes  & 0.6, 0.02, 0.1, 0.2 & 0.6, 0.02, 0.1, 0.2 \\
(Intergenic, UTR, CDS, Intron) & & \\
Geenuff error rate & 0.1 (+- 0.02) & 0.3 (+- 0.02) \\
Average genome size in Gbp& 1.1 (+- 0.5) & 0.3 (+- 0.1) \\
Average gene length & 23000 (+- 5000) & 3370 (+- 50) \\
\botrule
\end{tabular}}{Values are averages across all genomes of a data group. The genome size is excluding FASTA sequences without a gene and subsequences that were masked as completely erroneous.}
\end{table}

\begin{table}[!t]
\processtable{Data group statistics for our training data\label{Tab:statistics_training}} {
\begin{tabular}{@{}lll@{}}
\toprule & EnsemblMetazoa & JGI Phytosome\\
\midrule
Fraction of classes  & 0.6, 0.02, 0.1, 0.2 & 0.6, 0.02, 0.1, 0.2 \\
(Intergenic, UTR, CDS, Intron) & & \\
Geenuff error rate & 0.1 (+- 0.02) & 0.3 (+- 0.02) \\
Average genome size in Gbp& 1.1 (+- 0.5) & 0.3 (+- 0.1) \\
Average gene length & 23000 (+- 5000) & 3370 (+- 50) \\
\botrule
\end{tabular}}{Values are averages across all genomes of a data group. The genome size is excluding FASTA sequences without a gene and subsequences that were masked as completely erroneous.}
\end{table}

@@

\begin{table}[!t]
\processtable{Experimental Results and Comparison\label{Tab:03}} {
\begin{tabular}{@{}lll@{}}
\toprule & EnsemblMetazoa & JGI Phytosome\\
\midrule
Augustus & 0.62 (+-0.02) & 0.83 (+- 0.03)\\
Dilated CNN Baseline & 0.62 (+-0.02) & 0.83 (+- 0.03)\\
Best Helixer model & 0.62 (+-0.02) & 0.72 (+-0.02) \\
Best model + varied input length & 0.62 (+-0.02) & 0.72 (+-0.02) \\
Best model + varied input length + overlapping & 0.62 (+-0.02) & 0.72 (+-0.02) \\
Varied input length + overlapping + ensembling & 0.62 (+-0.02) & 0.72 (+-0.02) \\
\botrule
\end{tabular}}{Values are averages in CDS F1 (?) across all validation and test genomes of the \\ respective group.}
\end{table}

@@

\section{Results}

We propose a framework to develop a gene calling model that is both more general in the range genomes it can annotate and also outperforms traditional methods on a base pair wise evaluation. The overall results of Helixer, Augustus and a baseline build with dilated convolutional layers are shown in table \ref{Tab:03}.
